---
title: "sample_run_54188"
output: html_notebook
date: "2025-02-12"
---

This notebook analyzes capture-mark-recapture data using the *mrmr* and *mrmrmr* packages.

## Install the mrmr and mrmrmr packages

```{r}

# install cmdstanr and cmdstan
remotes::install_github("stan-dev/cmdstanr")
cmdstanr::install_cmdstan(overwrite = TRUE)

# install mrmr and mrmrmr
remotes::install_github("SNARL1/mrmr")
remotes::install_github("john-imperato/mrmrmr")

```

## Load required packages

```{r}

library(dplyr)
library(readr)
library(tibble)
library(cmdstanr)
library(mrmr)
library(mrmrmr)
library(patchwork)
library(bayesplot)

```

## Create required data sets

```{r}

captures <- read_csv(here::here("data", "54188_capture.csv"))
surveys <- read_csv(here::here("data", "54188_survey.csv"))

```

## Clean data with mrmr

```{r}

data_54188_TVD <- mrmr::clean_data(captures, surveys)

```

## Fit model with session-specific detection probabilities

```{r}

model_54188_TVD <- mrmrmr::fit_model_TVD(data = data_54188_TVD,
                                            chains = 4,
                                            parallel_chains = 4,
                                            threads_per_chain = 2,
                                            adapt_delta = 0.99)

write_rds(model_54188_TVD, here::here("sample_run", "54188_model_TVD.rds"))

```

```{r}

summary_54188 <- model_54188_TVD$m_fit$summary()

View(summary_54188)

```

### Diagnose potential non-convergence of the MCMC algorithm

-   Inspect traceplots and parameter summary table. In table, are any R~hat~ values $\ge 1.01$?

```{r model-diagnostics}
pars_to_plot <- c('alpha_lambda', 
                  'sigma_lambda', 
                  'beta_phi', 
                  'sigma_phi', 
                  'beta_detect')
bayesplot::mcmc_trace(model_54188_TVD$m_fit$draws(pars_to_plot))

model_54188_TVD$m_fit$summary(pars_to_plot)
```
